Generalized Plackett-Luce Likelihoods

### 2022-08-05 inst/jss_hyper3.Rnw
typo

If we allow non-finishers [that is, a subset of competitors who are
classified as being beaten by any finishing competitors], there is
another nontrivial order statistic, viz $a\succ b\succ\left\lbrace
a,b\right\rbrace$ [thus one of the two $a$'s won, one of the $b$'s
came second, and one of each of $a$ and $b$ failed to finish].

>>>>

If we allow non-finishers [that is, a subset of competitors who are
beaten by all the ranked competitors], there is another nontrivial
order statistic, viz $a\succ b\succ\left\lbrace a,b\right\rbrace$
[thus one of the two $a$'s won, one of the $b$'s came second, and one
of each of $a$ and $b$ failed to finish].
